\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-14 papers/itsc_2012/final.tex
suggested changes to sect 5

Currently agents cannot switch lanes. AORTA allows merging lanes by treating
the merge point as an intersection. \commentpk{i take it this is an orphan
paragraph?} \commentd{yeah, where should it belong?}

@@

Every step, a generator creates some number of new agents. If the agent's route
policy needs computation like pathfinding to operate, the generator either
performs it immediately (incurring a delay in simulation if it is running) or,
if possible, sends it to a pool of worker threads to process in the background.

Once an agent's route is ready, the agent waits alongside its starting lane (as
if it is in a driveway or parking lot). When the lane has no agents that could
potentially crash with the new vehicle, the new agent enters the system with
zero initial speed. Because behaviors must enforce speed limit along a lane
from the moment an agent enters a road, it is safe for a new agent to enter a
road if there is no other agent within the worst-case distance (traveling
distance at the speed limit, plus stopping distance from this speed) preceeding
the spawn point.% To avoid predicting which agents might enter the lane in the
%near future, there is a buffer space at the beginning of the lane where a new
%agent may never spawn. This disqualifies some short lanes from being spawn
%points, but this is not a big limitation in practice. \commentpk{I understand
%your concern about explaining the entire methodology, but the last 2 lines are
%unnecessary and somewhat distracting}

@@

All traversables (lanes and the straight line-approximation of turns) maintain
an ordered queue of occupying agents. One simulation step happens atomically,
meaning collision checking occurs after all agents have moved. If this were not
the case, false positives could occur when an agent steps before the agent in front
of it. A collision is defined as the reversal of order of agents during a step.

@@

\subsection{Agent Behavior}
\label{sec:behaviors}

Each agent has a \emph{behavior} governing it, responsible for obeying
intersection policies and avoiding collisions. When the agent travels past the
end of a lane during its step, the behavior picks the turn to take. At each
step, the behavior can make the agent react by performing one of two actions:
disappearing from the map (when the agent is at rest and is done with its route)
or setting an acceleration for the next step. Were lane changing modeled, that
would be another possible action.

The default behavior maximizes acceleration while obeying speed limits,
avoiding collisions, and obeying intersections. By considering the highest speed
achievable at the end of the next step and the subsequent stopping distance at
this speed, the behavior's lookahead engine can scan sufficiently far ahead
along several traversables to locate agents to avoid and intersections to query.
The analysis short-circuits at the first nearby agent and intersection requiring
a stop, since it would be illegal to drive further anyway.

\subsection{Simulation Limitations: Gridlock}

@@

There are three main components of the simulation, each configurable by
extending built-in implementations of an interface: agent behaviors, routing
strategies, and intersection policies. Behaviors have been described already in
section \ref{sec:behaviors}.

@@

Intersection policies are one of the most intriguing aspects of the simulation
to tweak, especially in light of autonomous vehicles. Current policies include
traditional stop signs, traffic signals, and an AIM-inspired autonomous
reservation system \cite{JAIR08-dresner}. The traffic signals are further
extensible by assigning groups of non-conflicting turns at each intersection
with some duration and offset. The experiment in section \ref{sec:results}
features standard turn grouping (turns from parallel incoming directions are
scheduled simultaneously, and left turns are grouped) and a breadth-first search
heuristic for propagating timings. Future policies could include signals that
adapt timings and refinements to the autonomous reservation policy.

@@

\subsection{Experiment parameters}

Each policy has parameters, so the configuration used is relevant. Stop signs
accept agents FCFS, refusing agents until they have idled at 0 speed for 1
second. This delay approximates human reaction time. The traffic signal policy
requires timings and groups of simultaneous turns for each intersection. The
configuration tested here uses a breadth-first search from one major road's
lanes to try to synchronize green signals for the agents near that lane to not
stop for several intersections. This heuristic needs improvement in how it
handles the remaining groups of turns that are scheduled after the first
sequence. Finally, the autonomous reservation policy allows new agents to join
existing groups of agents if their turn is compatible with the others. To
prevent one heavy direction of traffic from hogging the intersection
indefinitely, a timeout preemptively cycles through reservations. Ideally this
should be based on the relative numbers of agents depending on their
group of reservations.

>>>>

@@

Every step, a generator creates some number of new agents. If the agent's route
policy needs computation like pathfinding to operate, the generator either
performs it immediately (incurring a delay in simulation if it is running) or,
if possible, sends it to a pool of worker threads to process in the background.
Once an agent's route is ready, the agent waits alongside its starting lane (as
if it is in a driveway or parking lot). When the lane has no agents that could
potentially crash with the new vehicle, the new agent enters the system with
zero initial speed. % Because behaviors must enforce speed limit along a lane
%from the moment an agent enters a road, it is safe for a new agent to enter a
%road if there is no other agent within the worst-case distance (traveling
%distance at the speed limit, plus stopping distance from this speed) preceeding
%the spawn point. To avoid predicting which agents might enter the lane in the
%near future, there is a buffer space at the beginning of the lane where a new
%agent may never spawn. This disqualifies some short lanes from being spawn
%points, but this is not a big limitation in practice. \commentpk{I understand
%your concern about explaining the entire methodology, but the last 2 lines are
%unnecessary and somewhat distracting}

@@

All traversables (lanes and the straight line-approximation of turns) maintain
an ordered queue of occupying agents. A collision is detected when two agents
reverse order after a time step has completed.
\commentpk{Also do we still have point vehicles only?}
\commentd{Technically yes, but we could add in a check to make sure the fronts
  of every vehicle aren't too close to any other vehicle. It would just be
  needlessly expensive, and we trust the following-distance behavior.}

@@

\subsection{Agent Behavior}

Each agent has a \emph{behavior} governing it, responsible for obeying
intersection policies and avoiding collisions. When the agent travels past the
end of a lane during its step, the behavior picks the turn to take. At each
step, the behavior can make the agent react by performing one of two actions:
disappearing from the map (when the agent is at rest and is done with its route)
or setting an acceleration for the next step.

\subsection{Simulation Limitations}

Currently agents cannot change lanes. However, AORTA supports roads forcibly
merging by treating the merge point as an intersection. The lack of
lane-changing causes a second issue: gridlock.

@@

There are three main components of the simulation, each configurable by
extending built-in implementations of an interface: agent behaviors, routing
strategies, and intersection policies.

\section{Agent Behaviors}

\commentd{So is this paragraph below still relevant?}
The default behavior maximizes acceleration while obeying speed limits,
avoiding collisions, and obeying intersections. By considering the highest speed
achievable at the end of the next step and the subsequent stopping distance at
this speed, the behavior's lookahead engine can scan sufficiently far ahead
along several traversables to locate agents to avoid and intersections to query.
The analysis short-circuits at the first nearby agent and intersection requiring
a stop, since it would be illegal to drive further anyway.

@@

Intersection policies are one of the most intriguing aspects of the simulation
to tweak, especially in light of autonomous vehicles. Current policies include
traditional stop signs, traffic signals, and an AIM-inspired autonomous
reservation system \cite{JAIR08-dresner}. The traffic signals are further
extensible by assigning groups of non-conflicting turns at each intersection
with some duration and offset. Future policies could include signals that adapt
timings and refinements to the autonomous reservation policy.

@@

\subsection{Intersection Policies Evaluated}

Stop signs accept agents FCFS, refusing agents until they have idled at 0 speed
for 1 second. This delay approximates human reaction time.

The traffic signal policy requires timings and groups of simultaneous turns for
each intersection. The heuristic evaluated uses standard turn groups (turns from
parallel incoming directions are scheduled simultaneously, and left turns are
grouped) and employs propagates timings with a breadth-first search. The goal is
to synchronize green signals so agents in some lanes do not stop for several
intersections.

\commentd{advice on wording?}
Finally, in anticipation of the advent of autonomous vehicles, an autonomous
reservation policy inspired by AIM \cite{JAIR08-dresner} is tested. This policy
allows new agents to join existing groups of agents if their turn is compatible
with the others. To prevent one heavy direction of traffic from hogging the
intersection indefinitely, a timeout preemptively cycles through reservations.
Ideally this should be based on the relative numbers of agents depending on
their group of reservations. \commentd{take out the last sentence? all of the
policies could use some work.}
